UQWorld: an Applied UQ Community

### 2019-05-08 latex/uqworld-presentation.tex
Minor edit

\begin{tabularx}{\textwidth}{XXXX}
  \hline
                                    & Inception    & Establishment  & Maturity \\
  \hline
  \footnotesize{Majority of members}
  & Core members
  & UQLab users, UQ practitioners
  & UQ practitioners and researchers  \\

@@

  \footnotesize{Why members join}
  & Relationship with core members, problems with UQLab
  & matched interests in UQ, tangible value (info, support)
  & Tangible value: info, support, and social (incl. sharing expertise) \\
%  \footnotesize{Example of tasks}
%  & Define scope and goal, invite members, initiate discussions, prompt participation
%  & Write contents (about the community), organize \emph{activities} 
%  & off-line gatherings, manage volunteer (non core members)  \\ 
  \hline
\end{tabularx}

>>>>

\begin{tabularx}{\textwidth}{XXXX}
  \hline
                                    & Inception    & Establishment  & Maturity \\
  \hline
  \footnotesize{Majority of members}
  & Core members, UQLab users
  & UQLab users, UQ practitioners
  & UQ practitioners and researchers  \\

@@

  \footnotesize{Why members join}
  & Direct invitation, problems with UQLab
  & matched interests in UQ, tangible value (info, support)
  & Tangible value: info, support, and social (incl. sharing expertise) \\
%  \footnotesize{Example of tasks}
%  & Define scope and goal, invite members, initiate discussions, prompt participation
%  & Write contents (about the community), organize \emph{activities} 
%  & off-line gatherings, manage volunteer (non core members)  \\ 
  \hline
\end{tabularx}
